Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-17 paper.tex
update

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both aspects.

\cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.

A heuristic service composition method is proposed by Qi et al. \cite{qi2010combining} for QoS-aware web service composition, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. Obviously, there exists scalability problem for enumeration techniques.

Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions. Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions. A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution. These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

Few works \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured by the quality of semantic links that requires formal definition of ontology in Description Logic. This evaluation takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.

In summary, composition solutions from semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} does not consider QoS, and QoS-aware web service composition
\cite{gupta2015optimization,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing,pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

>>>>

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, this evaluation approach does not guarantee optimised qualities of composition solutions for QoS.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. but there exists scalability problems for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution. These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

Few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured by the quality of semantic links that requires formal definition of ontology in Description Logic. This evaluation takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches. There is a lack of a general approaches that achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a POS-based method with explicit support for the comprehensive model to find optimal compositions.
